### 2023-02-05 README.Rmd
Update `readme` to introduce `export_granlist` [no ci]

@@

The object can be used to recreate the computational environment via [Rocker](https://github.com/rocker-org/rocker). Please note that the oldest R version one can get from Rocker is R 3.1.0.

>>>>

The resolved result is an S3 object called `granlist` and can be exported as an installation script. The installation script can be execute on a vanilla R installation.

```r
export_granlist(graph, "gran.R")
```

However, the execution of the installation script often fails (now) due to missing system dependencies and incompatible R versions. Therefore, the approach outlined below should be used.

@@

A `granlist` object can be used to recreate the computational environment via [Rocker](https://github.com/rocker-org/rocker). Please note that the oldest R version one can get from Rocker is R 3.1.0.
